---
title: "Stephen Curry Statistics"
output: html_document
---

```{r, message=F, echo=F,warning=FALSE}
require(tidyr)
require(dplyr)
require(stringr)
require(readr)
require(lubridate)
require(readr)
require(janitor)
require(kableExtra)
require(purrr)
require(readxl)
require(lazyeval)
require(ggplot2)
require(broom)
require(plotly)
all_data <- read_excel("All Data Long.xlsx") %>% 
  clean_names()
comps <- "Comps.xlsx" %>% 
  excel_sheets() %>% 
  map(~read_excel(path = "Comps.xlsx", sheet = .)) 
for(i in 1:6){
  comps[[i]] <- comps[[i]] %>% 
    select(-1) %>% 
    mutate(scenario = excel_sheets("Comps.xlsx")[i])
}
comps <- bind_rows(comps) %>% 
  clean_names()

teams <- comps %>% 
  distinct(opp) %>% 
  arrange(opp)
```

# {.tabset}
## Home Game and Away Analysis {.tabset}
### Comparison of Overall Statistics
```{r,message=F, echo=F,warning=FALSE}
format <- function(game_var, value_var){
  filter_criteria = interp(~!is.na(x), x = as.name(value_var))
  temp <- comps %>% 
    filter_(filter_criteria) %>% 
    distinct_(~statistic, interp(~x, x = as.name(game_var)), 
              interp(~x, x = as.name(value_var)), ~sum_stat) %>% 
  arrange(statistic) %>% 
  spread(key = sum_stat, value = as.name(value_var)) %>% 
  mutate(mean_std =ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(mean*100, 2), "%"),
                    paste0(round(mean, 2)," (", round(std, 2),")")),
         med = ifelse(str_detect(pattern = "%", statistic),
                              paste0(base::format(median*100,nsmall = 2),"%"),
                                        round(median,2)),
         max = ifelse(str_detect(pattern = "%", statistic),
                                        paste0(base::format(max*100,nsmall = 2),"%"),
                                        round(max,2)),
         min = ifelse(str_detect(pattern = "%", statistic),
                                        paste0(base::format(min*100,nsmall = 2),"%"),
                                        round(min,2))) %>%
  select(-std)
  return(temp)
}
home_stats <- format(game_var = "n_games_home", value_var = "value_home")
away_stats <- format(game_var = "n_games_away", value_var = "value_away")
all_stats <- format(game_var = "n_games_all", value_var = "value_all")

stats <- all_stats %>%  
  left_join(home_stats, by = "statistic",suffix = c("", "_h")) %>% 
  left_join(away_stats, by = "statistic",suffix = c("", "_a")) %>% 
  select(statistic, contains("n_games"),contains("mean_std"),contains("mean"), contains("std"), contains("med"),
         contains("min"), contains("max")) %>%
  mutate(order = case_when(statistic == "+/-" ~1,
                           str_detect(pattern = "PT", statistic) ~ 2,
                           str_detect(pattern = "3P%", statistic) ~ 3.1,
                           str_detect(pattern = "3P", statistic) ~ 3,
                           str_detect(pattern = "FG%", statistic) ~ 4.1,
                           str_detect(pattern = "FG", statistic) ~ 4,
                           str_detect(pattern = "FT%", statistic) ~ 5.1,
                           str_detect(pattern = "FT", statistic) ~ 5,
                           statistic == "AST" ~6,
                           statistic == "ORB" ~ 7,
                           statistic == "TOV" ~7.1,
                           statistic == "BLK" ~8,
                           statistic == "STL" ~9,
                           TRUE  ~ 10)) %>% 
  arrange(order, statistic) %>% 
  mutate(mean_std_h =cell_spec(mean_std_h, format = "html", color = ifelse(mean_h < mean, "red", "green")),
         mean_std_a =cell_spec(mean_std_a, format = "html", 
                               color = ifelse(mean_a < mean, "red", "green")),
         statistic = cell_spec(statistic, format = "html",bold = T),
         med_h =cell_spec(med_h, format = "html", color = 
                            ifelse(median_h < median |(statistic == "TOV" & median_h >= median), 
                                                                 "red", "green")),
         med_a =cell_spec(med_a, format = "html", color = 
                            ifelse(median_a < median|(statistic == "TOV" & median_a >= median), 
                                                                 "red", "green")),
         mean_std = cell_spec(mean_std, italic = T),
         med = cell_spec(med,italic = T)) %>% 
  select(-mean, -mean_h, -mean_a, -contains("median"),-contains("min"),-contains("max"),-order)

kable(stats, format = "html",align = "c", escape = F,
      col.names = c("Metric", rep(c("Overall", "Home", "Away"), 3))) %>% 
  kable_styling(bootstrap_options = c("striped", "hover")) %>% 
  add_header_above(header = c("", "Number of Games" = 3, "Mean (SD)/Percentage" = 3, "Median" = 3)) %>% 
  pack_rows(group_label = "Plus-Minus", start_row = 1, 1) %>% 
  pack_rows(group_label = "Scoring", start_row = 2, 11) %>% 
  pack_rows(group_label = "Other Offense", start_row = 12, 14) %>% 
  pack_rows(group_label = "Defense", start_row = 15, 18) %>% 
  scroll_box(width = "700px", height = "500px") 
```

<b>Notes:</b><br>
[1] Note that field goal, free throw, and three point percentage statistics are calculated out of all games that Steph attempted at least one of that type of shot. All other statistics are measured out of all the total number of games that Steph has played over his career.<br>
[2] Green denotes metrics that Steph rates higher in home or away games than his typical career performance, and red denotes metrics that Steph rates lower in.<br>

### Teamwise Comparison
#### Choose a Team: {.tabset .tabset-dropdown}
##### Atlanta Hawks
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
format_tm <- function(team){
  temp <- comps %>% 
    filter(opp == teams$opp[i]) %>% 
    distinct(statistic, sum_stat, value, n_games, location) %>% 
  arrange(statistic, sum_stat, location) 
  temp_h <- temp %>% 
    filter(location == "Home") %>% 
    spread(sum_stat, value) %>% 
    mutate(mean_std =ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(mean*100, 2), "%"),
                    paste0(round(mean, 2)," (", round(std, 2),")")),
           med_fmt = ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(median*100, 2), "%"), round(median, 2)))
  temp_a <- temp %>% 
    filter(location == "Away") %>% 
    spread(sum_stat, value) %>% 
     mutate(mean_std =ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(mean*100, 2), "%"),
                    paste0(round(mean, 2)," (", round(std, 2),")")),
            med_fmt = ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(median*100, 2), "%"), round(median, 2)))
  temp_o <- temp %>% 
    filter(location == "All Games") %>% 
    spread(sum_stat, value) %>% 
    mutate(mean_std =ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(mean*100, 2), "%"),
                    paste0(round(mean, 2)," (", round(std, 2),")")),
           med_fmt = ifelse(str_detect(pattern = "%", statistic),
                    paste0(round(median*100, 2), "%"), round(median, 2)))
  temp_out <- temp_o %>% 
    left_join(temp_h, by = "statistic", suffix = c("", "_h")) %>% 
    left_join(temp_a, by = "statistic", suffix = c("", "_a")) %>%
    select(statistic, contains("n_games"),contains("mean_std"),contains("mean"), contains("std"), contains("med"), contains("min"), contains("max")) %>% 
  mutate(order = case_when(statistic == "+/-" ~1,
                           str_detect(pattern = "PT", statistic) ~ 2,
                           str_detect(pattern = "3P%", statistic) ~ 3.1,
                           str_detect(pattern = "3P", statistic) ~ 3,
                           str_detect(pattern = "FG%", statistic) ~ 4.1,
                           str_detect(pattern = "FG", statistic) ~ 4,
                           str_detect(pattern = "FT%", statistic) ~ 5.1,
                           str_detect(pattern = "FT", statistic) ~ 5,
                           statistic == "AST" ~6,
                           statistic == "ORB" ~ 7,
                           statistic == "TOV" ~7.1,
                           statistic == "BLK" ~8,
                           statistic == "STL" ~9,
                           TRUE  ~ 10)) %>%
  arrange(order, statistic) %>%
  mutate(mean_std_h =cell_spec(mean_std_h, format = "html", color = ifelse(mean_h < mean, "red", "green")),
         mean_std_a =cell_spec(mean_std_a, format = "html",
                               color = ifelse(mean_a < mean | (statistic == "TOV" & mean_h >= mean),
                                                                 "red", "green")),
         statistic = cell_spec(statistic, format = "html",bold = T),
         med_fmt_h =cell_spec(med_fmt_h, format = "html", color =
                            ifelse(median_h < median |(statistic == "TOV" & median_h >= median),
                                                                 "red", "green")),
         med_fmt_a =cell_spec(med_fmt_a, format = "html", color =
                            ifelse(median_a < median|(statistic == "TOV" & median_a >= median),
                                                                 "red", "green")),
         mean_std = cell_spec(mean_std, italic = T),
         med_fmt = cell_spec(med_fmt,italic = T)) %>%
  select(-mean, -mean_h, -mean_a, -contains("median"),-contains("min"),-contains("max"),-order,-starts_with("std"))
  n_stats_better <- temp_o %>% 
    left_join(temp_h, by = "statistic", suffix = c("", "_h")) %>% 
    left_join(temp_a, by = "statistic", suffix = c("", "_a")) %>%
    select(-contains("std"), -contains("fmt"),-contains("min"),-contains("max"),-contains("games"),
           -contains("loc")) %>% 
    mutate(mean_better_a = case_when(statistic == "TOV" ~ ifelse(mean_a < mean, 1, 0),
                                     mean_a > mean ~ 1,
                                     T ~ 0),
           mean_better_h = case_when(statistic == "TOV" ~ ifelse(mean_h < mean, 1, 0),
                                     mean_h > mean ~ 1,
                                     T ~ 0),
           med_better_a = case_when(statistic == "TOV" ~ ifelse(median_a < median, 1, 0),
                                     median_a > median ~ 1,
                                     T ~ 0),
           med_better_h = case_when(statistic == "TOV" ~ ifelse(median_h < median, 1, 0),
                                     median_h > median ~ 1,
                                     T ~ 0)) %>% 
    select(contains("better"),statistic) %>% 
    summarise(mean_std_a = as.character(sum(mean_better_a)),
              mean_std_h = as.character(sum(mean_better_h)),
              med_fmt_a = as.character(sum(med_better_a)),
              med_fmt_h = as.character(sum(med_better_h))) %>% 
    mutate(statistic = "<b>Number Stats Better</b>")

temp_out2 <- temp_out %>% 
  bind_rows(n_stats_better)
return(temp_out2)
}

format_kbl <- function(df, team){
  tbl <- kable(df, format = "html",align = "c", escape = F,
      col.names = c("Metric", rep(c("Overall", "Home", "Away"), 3))) %>% 
  kable_styling(bootstrap_options = c("striped", "hover")) %>% 
  add_header_above(header = c("", "Number of Games" = 3, "Mean (SD)/Percentage" = 3, "Median" = 3)) %>% 
  pack_rows(group_label = "Plus-Minus", start_row = 1, 1) %>% 
  pack_rows(group_label = "Scoring", start_row = 2, 11) %>% 
  pack_rows(group_label = "Other Offense", start_row = 12, 14) %>% 
  pack_rows(group_label = "Defense", start_row = 15, 18) %>% 
  pack_rows(group_label = "Overall Performance", start_row = 19, 19) %>% 
  scroll_box(width = "700px", height = "500px") 
  return(tbl)
}
i = 1
format_kbl(format_tm(teams$opp[i]))

```

##### Boston Celtics
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Brooklyn Nets
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Charlotte Hornets
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Chicago Bulls
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Cleveland Cavaliers
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Dallas Mavericks
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Denver Nuggets
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Detroit Pistons
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Houston Rockets
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Indiana Pacers
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Los Angeles Clippers
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Los Angeles Lakers
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Memphis Grizzlies
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Miami Heat
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Milwaukee Bucks
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Minnesota Timberwolves
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### New Orleans Pelicans
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### New York Knicks
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Oklahoma City Thunder
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Orlando Magic
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Philadelphia 76ers
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Phoenix Suns
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Portland Trailblazers
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Sacramento Kings
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### San Antonio Spurs
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Toronto Raptors
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Utah Jazz
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

##### Washington Wizards
```{r,message=F, echo=F,warning=FALSE}
opts <- options(knitr.kable.NA = "")
i = i + 1
format_kbl(format_tm(teams$opp[i]))
```

### Statistical Comparisons # {.tabset}
#### Team  vs. All Games # {.tabset}
##### Points Per Game
```{r,message=F, echo=F,warning=FALSE}
run_test <- function(stat, alpha,stat_label, loc){
  stat_data <- all_data %>% 
    filter(statistic == stat, location %in% loc)
  out_data <- tibble()
  for (i in 1:29){
    team_data <- stat_data %>% 
      filter(opp == teams$opp[i])
    rest_data <- stat_data %>% 
      filter(opp != teams$opp[i])
    team_summary <- team_data %>% 
      mutate(avg_stat = mean(value),
             med_stat = median(value)) %>% 
      distinct(avg_stat,med_stat)
    all_summary <- rest_data %>% 
      mutate( avg_stat = mean(value),
             med_stat = median(value)) %>% 
      distinct(avg_stat,med_stat)
    results <- tidy(wilcox.test(team_data$value,rest_data$value)) %>% 
      mutate(opp = teams$opp[i]) %>% 
      select(-method, -alternative) %>% 
      bind_cols(all_summary) %>% 
      bind_cols(team_summary) %>% 
      rename(avg_stat_tm = avg_stat1,
             med_stat_tm = med_stat1) %>% 
      select(opp,statistic, p.value, starts_with("avg"), starts_with("med"))
    out_data <- out_data %>% 
      bind_rows(results)
  }
  out_data2 <- out_data %>% 
    mutate(sig = ifelse(p.value < alpha, "*", "")) %>% 
    arrange(desc(sig)) 
  red_rows <- which((out_data2$med_stat_tm < out_data2$med_stat) & out_data2$sig =="*")
  green_rows <- which((out_data2$med_stat_tm >= out_data2$med_stat) & out_data2$sig =="*")
  out_data_fmt <- kable(out_data2, format = "html",
                        col.names = c('Team','Test Statistic', 'P-Value','Mean - All', 'Mean - Team',
                                      'Median - All', 'Median - Team',""), align = 'c',digits = 2,
                        label = stat_label) %>% 
    kable_styling(bootstrap_options = c("striped", "hover")) %>% 
    row_spec(red_rows, color = "red") %>% 
    row_spec(green_rows, color = "green") %>% 
    add_footnote(label = c("* indicates significance at the 95% confidence level.","Green indicates relative worse performance against the team, and red indicates relative better performance."),notation = "number")
  return(out_data_fmt)
}
run_test("PTS", 0.05, stat_label = "Points Per Game", loc =c("Home", "Away")) 
```

##### Plus/Minus
```{r,message=F, echo=F,warning=FALSE}
run_test("+/-", 0.05, stat_label = "Plus/Minus",loc =c("Home", "Away"))
```

##### FG%
```{r,message=F, echo=F,warning=FALSE}
run_test("FG%", 0.05, stat_label = "Field Goal Percentage",loc =c("Home", "Away"))
```

##### 3P%
```{r,message=F, echo=F,warning=FALSE}
run_test("3P%", 0.05, stat_label = "Three Point Percentage",loc =c("Home", "Away"))
```

##### FT%
```{r,message=F, echo=F,warning=FALSE}
run_test("FT%", 0.05, stat_label = "Free Throw Percentage",loc =c("Home", "Away"))
```

#### Team Away vs. All Away # {.tabset}
##### Points Per Game
```{r,message=F, echo=F,warning=FALSE}
run_test("PTS", 0.05, stat_label = "Points Per Game", loc =c("Away"))
```

##### Plus/Minus
```{r,message=F, echo=F,warning=FALSE}
run_test("+/-", 0.05, stat_label = "Plus/Minus",loc =c("Away"))
```

##### FG%
```{r,message=F, echo=F,warning=FALSE}
run_test("FG%", 0.05, stat_label = "Field Goal Percentage",loc =c("Away"))
```

##### 3P%
```{r,message=F, echo=F,warning=FALSE}
run_test("3P%", 0.05, stat_label = "Three Point Percentage",loc =c("Away"))
```

##### FT%
```{r,message=F, echo=F,warning=FALSE}
run_test("FT%", 0.05, stat_label = "Free Throw Percentage",loc =c("Away"))
```

#### Team Home vs. All Home # {.tabset}
##### Points Per Game
```{r,message=F, echo=F,warning=FALSE}
run_test("PTS", 0.05, stat_label = "Points Per Game", loc =c("Home"))
```

##### Plus/Minus
```{r,message=F, echo=F,warning=FALSE}
run_test("+/-", 0.05, stat_label = "Plus/Minus",loc =c("Home"))
```

##### FG%
```{r,message=F, echo=F,warning=FALSE}
run_test("FG%", 0.05, stat_label = "Field Goal Percentage",loc =c("Home"))
```

##### 3P%
```{r,message=F, echo=F,warning=FALSE}
run_test("3P%", 0.05, stat_label = "Three Point Percentage",loc =c("Home"))
```

##### FT%
```{r,message=F, echo=F,warning=FALSE}
run_test("FT%", 0.05, stat_label = "Free Throw Percentage",loc =c("Home"))
```

## Yearly Growth # {.tabset}
### Points Scored
```{r,message=F, echo=F,warning=FALSE}
plot_data <- function(stat,stat_label){
  df <- all_data %>% 
    filter(statistic == stat) %>% 
    mutate(date = as.Date(date))
  reg <- lm(data = df, formula = value ~ date)
  plt <- ggplot(df, mapping = aes(x = date, y = value, color = season)) +
    geom_point() + 
    ggtitle(paste0(stat_label, " Over Time")) +
    xlab("Date") + 
    ylab(stat_label) +
    labs(color = "Season") +
    geom_abline(slope = reg$coefficients[2], intercept = reg$coefficients[1])
  return(ggplotly(plt))
}
plot_data("PTS", "Points Scored")

```

### Plus/Minus
```{r,message=F, echo=F,warning=FALSE}
plot_data("+/-", "Plus/Minus")
```

### FG%
```{r,message=F, echo=F,warning=FALSE}
plot_data("FG%", "FG%")
```

### 3P%
```{r,message=F, echo=F,warning=FALSE}
plot_data("3P%", "3P%")
```

### FT%
```{r,message=F, echo=F,warning=FALSE}
plot_data("FT%", "FT%")
```

## Performance v Game Result # {.tabset}
### Logistic Regression Model
```{r,message=F, echo=F,warning=FALSE}
all_data_wide <- all_data %>% 
  mutate(result_binary = ifelse(result == "Win",1,0),
         year = year(date)) %>% 
  select(result_binary, statistic, value,date, season, location, series, year) %>% 
  spread(statistic,value)

glm <- glm(data = all_data_wide %>% select(-season,-series,-year,-date,-location), family = binomial(), result_binary ~.)
df <- tidy(glm) %>% 
  mutate(or = round(ifelse(str_detect(pattern = "Int", term), NA,exp(estimate)),2),
         or = ifelse(or < 1, cell_spec(or, format = "html", color = "red"),
                     cell_spec(or, format = "html", color = "green")),
         sig = ifelse(p.value < 0.05, "*", "")) %>% 
  select(-statistic)

kable(df, format = "html", digits = 2,col.names = c("Model Term",
                                                    "Estimate", "Standard Error","P-Value",
                                                    "Odds Ratio",""), escape = F,
      align = "c") %>% 
kable_styling(bootstrap_options = c("striped", "hover")) 
```

### Visualizations
```{r,message=F, echo=F,warning=FALSE}
plt <- ggplot(data = all_data, mapping = aes(x = result, y = value, fill = result)) +
  stat_summary(fun="mean", geom="bar") +
  theme(legend.position = "none") +
  xlab("Game Result") + 
  ylab("Statistic Value") +
  facet_wrap(~statistic)
ggplotly(plt)
```

